Scheduling and Vectorization for MPC

### 2022-03-02 paper_SIMD.tex
Yet another minor change, removed a TODO.
Answered Ishaq's question.

\ishaq{TODO: @Ana: I am still confused about what prevents a reviewer from saying, "you argue correctness of the schedule from unrolled MPC, you don't argue it for the pre-unrolled CFG that you use". Please comment.}

@@

The canonical dimensionality of \texttt{res} is 1. Also, the phi-node \texttt{res1 = PHI(res, res2)} is a target-less phi-node (the implication being that the inner for loop can be vectorized across $i$). After Phase 1, Basic vectorization produces the following code (statements are implicitly vectorized along $i$ and $j$). \ana{Define the interpretation of vectorized Update!}

>>>>

\ishaq{TODO: @Ana: I am still confused about what prevents a reviewer from saying, "you argue correctness of the schedule from unrolled MPC, you don't argue it for the pre-unrolled CFG that you use". Please comment.} \ana{The correctness proof answer this question. The unrolled schedule is the \emph{concretization} of MPC source. We define (1) the obvious $\gamma$, (2) we define partial order over MPC source codes (this is our abstract domain $A$), and (3) a partial order over unrolled schedules. Then we prove two theorems that $A \le A' \Rightarrow \gamma(A) \subseteq \gamma(A')$ and that the MPC source $\le$ Vectorized MPC source.}

@@

The canonical dimensionality of \texttt{res} is 1. Also, the phi-node \texttt{res1 = PHI(res, res2)} is a target-less phi-node (the implication being that the inner for loop can be vectorized across $i$). After Phase 1, Basic vectorization produces the following code (statements are implicitly vectorized along $i$ and $j$). In a vectorized update statement, we can ignore the incoming array, \texttt{res2} in this case. The update writes (in parallel) all locations of the 2-dimensional array, in this case it sets up each \texttt{res3[i,j] = tmp3[i,j]}.
